Make any stupid plot you want

### 2021-01-18 draft/sections/math.tex
triangularization section

\label{sec:base_data}
\begin{figure}[H]
    \includegraphics[width=\textwidth]{figures/math/k_different_types.png}
    \label{fig:base_space_types}
    \caption{The topological base space $K$ encodes the connectivity of the data space, for example if the data is independent points or a map or on a sphere}
\end{figure}

@@

\begin{figure}[H]
    \label{fig:base_space_div}
    \includegraphics[width=.5\linewidth]{figures/math/k_qspace.png}
    %%include second figure where fiber goes otherway
\end{figure}
The topology $K$ and the

@@

\begin{figure}[H]
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{figures/math/temp_1k.png}
        %% add box around neighboring P and Map
        \label{fig:base_example_line}
    \end{subfigure}
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{figures/math/temp_2k.png}
        \label{fig:base_example_plane}
    \end{subfigure}
    \label{fig:base_example}
    \caption{These two datasets have the same fiber of temperature but different base spaces. In figure~\ref{fig:base_example_line} the temperature values are 1D continuous, while in figure~\ref{fig:base_example_plane} the temperature values are 2D continuous.}
\end{figure}

@@

\begin{figure}[H]
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{figures/math/temp_2f.png}
        \label{fig:fiber_example_plane}
    \end{subfigure}
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{figures/math/temp_3f.png}
        \label{fig:fiber_example_cube}
    \end{subfigure}
    \label{fig:fiber_example}
    \caption{The fiber is expanded to include metadata fields that describe the semantics of $K$. In figure~\ref{fig:fiber_example_plane} the fiber is \textrm{temperature} $\times$ \textrm{time} and in figure~\ref{fig:fiber_example_cube} the fiber is \textrm{temperature}$\times$ \textrm{latitude} $\times$ {longitude}}.
\end{figure}

@@

\begin{figure}[H]
    \includegraphics[width=1\linewidth]{figures/math/fiberbundle.png}
    \label{fig:fiber_example_section}
    \caption{The section $\tau_1$ returns the blue points,  while $\tau_2$ returns the purple points. $\Gamma(E)$ is the set of all sections, including $\tau_1$ and $\tau_2$}.  
\end{figure}
Given the fiber described in equation~\ref{eq:fiber_plane}, the sections $\tau_{1}$ and $\tau_{2}$ in figure~\ref{fig:fiber_example_section} return tuples of the form
\begin{equation}
\tau(k) = (k, (temperature, time))
\end{equation}
such that sections with the constraint that time is monotonic return a timeseries.

@@

\subsubsection{{Example}}
\begin{figure}[H]
    \includegraphics[width=.4\linewidth]{figures/math/render.png}
    \caption{}
    \label{fig:render}
\end{figure}

@@

\subsubsection{Assembling Marks}
\begin{figure}[H]
    \includegraphics[width=\textwidth]{figures/math/path_of_q}
    \label{fig:artist_q}
    \caption{The $\nu$ functions convert data $E$ to visual $V$. $Q$ assembles the different types of visual parameters $V_{i}$ into a graphic in $H$. $Q\circ\mu(\xi^{-1}J)$ forms a visual mark by applying $Q$ to a region mapped to connected components $J \subset K$.}  
\end{figure}

@@

\begin{figure}[H]
    \includegraphics[width=\textwidth]{figures/math/diff_type_q.png}
    \label{fig:artist_mark_change}
\end{figure}

@@

\paragraph{Q: scatter plot}
\begin{figure}[H]
    \includegraphics[width=\textwidth]{figures/math/scatter.png}
    \label{fig:artist_scatter}
\end{figure}

@@

\paragraph{Q: line plot}
\begin{figure}[H]
    \includegraphics[width=\textwidth]{figures/math/line.png}
    \label{fig:artist_line}
\end{figure}

@@

\paragraph{Q: heatmap}
\begin{figure}[H]
    \includegraphics[width=\textwidth]{figures/math/heatmap.png}
    \label{fig:artist_heatmap}
\end{figure}
The heatmap in figure~\ref{fig:artist_heatmap} 
\begin{equation}
Q(xpos, ypos, color)
\end{equation}
has in the simple case a direct lookup into $K$ to obtain the $\mu = (x,y,c)$ values that are mapped into 
\begin{align}
D_{RGB} &= color(\xi(\alpha_1, \alpha_2))
D_x & = xpos(\xi(\alpha_1, \alpha_2))
D_y &= ypos(\xi(\alpha_1, \alpha_2))
\end{align}
through $\rho$.

@@

\subsection{Making the fiber bundle computable}
\label{sec:triangulization}
%% we can talk about triangulazation backwards from the mark
%% To implement this, we 
In our draft implementation of the data as fiber bundle model, we represent $K$ as a simplacial complex.

\begin{figure}[h!]
    \label{fig:simplex}
    \includegraphics{figures/math/simplex.png}
    \caption{Simplices can encode the connectivity of the data, from fully disconnected (0 simplex) observations to all observations are connected to at least 3 other observations}
\end{figure}

K is a triangularizable topological space; one triangularization scheme is as a set composed of simplices\cite{geometricaSimplicialComplexes}, such as those shown in figure~\ref{fig:simplex}.

@@

Given data that lies on a toroidal space as shown in figure~\ref{fig:triangle_torus}, in our model this structure can be implemented as a simplacial complex of two 2-simplexes. We unfold the torus into the two triangles that compose the square in figure~\ref{fig:artist_heatmap} and encode that as K. We also constrain the functions on $A$, $A^\prime$, $B$ and $B^\prime$ such that $A$ can be glued to $A^\prime$ and $B$ to $B^\prime$ to reconstruct the torus.

>>>>

\label{sec:base_data}
\begin{figure}[h!]
    \includegraphics[width=\textwidth]{figures/math/k_different_types.png}
    \label{fig:base_space_types}
    \caption{The topological base space $K$ encodes the connectivity of the data space, for example if the data is independent points or a map or on a sphere}
\end{figure}

@@

\begin{figure}[h!]
    \label{fig:base_space_div}
    \includegraphics[width=.5\linewidth]{figures/math/k_qspace.png}
    %%include second figure where fiber goes otherway
\end{figure}
The topology $K$ and the

@@

\begin{figure}[h!]
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{figures/math/temp_1k.png}
        %% add box around neighboring P and Map
        \label{fig:base_example_line}
    \end{subfigure}
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{figures/math/temp_2k.png}
        \label{fig:base_example_plane}
    \end{subfigure}
    \label{fig:base_example}
    \caption{These two datasets have the same fiber of temperature but different base spaces. In figure~\ref{fig:base_example_line} the temperature values are 1D continuous, while in figure~\ref{fig:base_example_plane} the temperature values are 2D continuous.}
\end{figure}

@@

\begin{figure}[h!]
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{figures/math/temp_2f.png}
        \label{fig:fiber_example_plane}
    \end{subfigure}
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{figures/math/temp_3f.png}
        \label{fig:fiber_example_cube}
    \end{subfigure}
    \label{fig:fiber_example}
    \caption{The fiber is expanded to include metadata fields that describe the semantics of $K$. In figure~\ref{fig:fiber_example_plane} the fiber is \textrm{temperature} $\times$ \textrm{time} and in figure~\ref{fig:fiber_example_cube} the fiber is \textrm{temperature}$\times$ \textrm{latitude} $\times$ {longitude}}.
\end{figure}

@@

\begin{figure}[h!]
    \includegraphics[width=1\linewidth]{figures/math/fiberbundle.png}
    \label{fig:fiber_example_section}
    \caption{The section $\tau_1$ returns the blue points,  while $\tau_2$ returns the purple points. $\Gamma(E)$ is the set of all sections, including $\tau_1$ and $\tau_2$}.  
\end{figure}
Given the fiber described in equation~\ref{eq:fiber_plane}, the sections $\tau_{1}$ and $\tau_{2}$ in figure~\ref{fig:fiber_example_section} return tuples of the form
\begin{equation}
\tau(k) = (k, (temperature, time))
\end{equation}
such that sections with the constraint that time is monotonic return a timeseries.

@@

\subsubsection{{Example}}
\begin{figure}[h!]
    \includegraphics[width=.4\linewidth]{figures/math/render.png}
    \caption{}
    \label{fig:render}
\end{figure}

@@

\subsubsection{Assembling Marks}
\begin{figure}[h!]
    \includegraphics[width=\textwidth]{figures/math/path_of_q}
    \label{fig:artist_q}
    \caption{The $\nu$ functions convert data $E$ to visual $V$. $Q$ assembles the different types of visual parameters $V_{i}$ into a graphic in $H$. $Q\circ\mu(\xi^{-1}J)$ forms a visual mark by applying $Q$ to a region mapped to connected components $J \subset K$.}  
\end{figure}

@@

\begin{figure}[h!]
    \includegraphics[width=\textwidth]{figures/math/diff_type_q.png}
    \label{fig:artist_mark_change}
\end{figure}

@@

\paragraph{Q: scatter plot}
\begin{figure}[h!]
    \includegraphics[width=\textwidth]{figures/math/scatter.png}
    \label{fig:artist_scatter}
\end{figure}

@@

\paragraph{Q: line plot}
\begin{figure}[h!]
    \includegraphics[width=\textwidth]{figures/math/line.png}
    \label{fig:artist_line}
\end{figure}

@@

\paragraph{Q: heatmap}
\begin{figure}[h!]
    \includegraphics[width=\textwidth]{figures/math/heatmap.png}
    \label{fig:artist_heatmap}
\end{figure}
The heatmap in figure~\ref{fig:artist_heatmap} 
\begin{equation}
Q(xpos, ypos, color)
\end{equation}
has in the simple case a direct lookup into $K$ to obtain the $\mu = (x,y,c)$ values that are mapped into 
\begin{align}
D_{RGB} &= color(\xi(\alpha_1, \alpha_2))
D_x & = xpos(\xi(\alpha_1, \alpha_2))
D_y &= ypos(\xi(\alpha_1, \alpha_2))
\end{align}
through $\rho$.

@@

\subsection{Making the fiber bundle computable}
\label{sec:triangulization}

\begin{figure}[h!]
    \includegraphics{figures/math/simplex.png}
    \caption{Simplices can encode the connectivity of the data, from fully disconnected (0 simplex) observations to all observations are connected to at least 3 other observations}
    \label{fig:triangle_simplex}
\end{figure}

One way to build reusable and flexible $\xi$ is to choose a consistent way of representing$K$. In our draft implementation of the data as fiber bundle model, we triangularize $K$ using complexes of the simplicies shown in figure~\ref{fig:triangle_simplex} such that $\xi$ consistently yields some combination of vertexes, edges, and faces. This gives a common data indexing structure on which to build the rest of $Q$.

@@

Given data that lies on the toroidal space shown in figure~\ref{fig:triangle_torus}, the torus $K$ can be implemented as a simplacial complex of two 2-simplexes. We unfold the torus into the two triangles that compose the square in figure~\ref{fig:artist_heatmap} and encode that as K. We also constrain the functions on $A$, $A^\prime$, $B$ and $B^\prime$ such that $A$ can be glued to $A^\prime$ and $B$ to $B^\prime$ to reconstruct the torus.
